CRUSE to Safe Cycling in Ireland

### 2023-09-14 paper.qmd
Add section x-refs

At the European Union level ...

In Ireland...

Mobility hub.

Business cases need evidence.

Como UK.

\[Gary, Suzanne, others input here please.\]

In this context, TII commissioned the CRUSE project which is...

The rest of paper is structured as follows...

# Methods

@@

# Results

@@

# Discussion

# Conclusions

>>>>

At the European level, the European Union has set a target of reducing greenhouse gas emissions by 55% by 2030, compared to 1990 levels, and to achieve 'net-zero' by 2050.^[
https://climateactiontracker.org/countries/eu/targets/
]
Regarding road traffic casualties, another deadly consequence of inefficient transport systems, the Road Infrastructure Safety Management (RISM) directive (2008/96/EC) requires member states to implement a road safety management system (RSMS) for all public roads.
Specifically, "Member States shall ensure that the ranking of high accident concentration sections and the network safety ranking are carried out".^[
https://eur-lex.europa.eu/legal-content/EN/TXT/?uri=celex%3A32008L0096
]
Given that 'safety' in this context is usefully quantified as the number of people killed and seriously injured (KSI) per distance travelled, the directive requires estimation of distance travelled by mode, down to the road link level.
For cycling, on which there is a paucity of data, this is a major challenge.

In Ireland, the Road Safety Authority (RSA) has set the target of halving the number of road traffic deaths and serious injuries by 2030.^[
https://www.drugsandalcohol.ie/35347/
]
Doing so while simultaneously enabling rapid uptake of active modes will require key active travel routes to be identified and improved.

<!-- \[Gary, Suzanne, others input here please.\] -->

It was in this context that TII commissioned the Cycle Route Uptake and Scenario Estimation (CRUSE) project.
Based on the Propensity to Cycle Tool (PCT) for England and Wales [@lovelace2017], the CRUSE tool was developed to provide evidence on current cycling levels and future cycling potential nationwide across Ireland.

The rest of paper is structured as follows. In @sec-methods, we outline the methods used to generate the evidence presented in the CRUSE tool for Ireland. In @sec-results, we present the results of the CRUSE tool, including estimates of current cycling levels and future cycling potential at the national, regional and local levels. In @sec-discussion, we discuss the implications of the results for policy and practice. In @sec-conclusions, we conclude the paper.

# Methods {#sec-methods}

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}

# Conclusions {#sec-conclusions}
